Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-10-19 paper/aldebaran.tex
conclusion

>>>>

With CARMA models we have confirmed the previously-suspected planet around Aldebaran using archival data, and additionally detected acoustic oscillations that permit a $\sim 6\%$ mass determination. We have confirmed both of these results with new ground-based observations, and space-based photometry with \ktwo.

From this pilot study with Aldebaran, have shown that with limited quantities of data of limited quality, we can nevertheless do precision asteroseismology from the ground and obtain very precise estimates of stellar parameters. Sufficient data either already exist, or are trivial to obtain, in order to do this for essentially all bright giants; while for solar-like stars, these new methods allow significantly relaxed observing requirements. Furthermore, CARMA models and related methods will enhance deep, all-sky photometric surveys such as \emph{Gaia} in space, or \emph{LSST} from the ground, from which many thousands of new asteroseismic determinations will be possible.
